\section{Experience}
    \cventry{2013-Present}{Software Development}{\textsc{Freelance}}{Various}{}{Helped clients figure out the needs and scope of their project when necessary. Designed their products over several steps of iteration, often working with a designer. Implemented custom backend functionality in existing products. Administered client databases, and currently providing maintenance through various project lifetimes.}
    \cventry{2014-Present}{Backend Development}{\textsc{Freelance}}{PriceWombat.com}{}{Iteratively improved a PHP web scraping framework to and developed scrapers to scan more than 70 online stores. Developed a Chrome extension to help existing and future users better take advantage of the service.}
    \cventry{2014-Present}{Administration \& Development}{\textsc{Principal Partner}}{Jiraffe Creative}{}{Primarily administrative activities including systems, database, DNS, and Google Apps domain administration, forming business entities, developing a business plan and marketing strategy. Other duties included front and back end web development, analytics, bug tracking, research and development, and copywriting.}
    \cventry{2015-Present}{Systems Administration}{\textsc{Freelance}}{FoxyTronics.com}{}{Enabled secure transport for web services and patched several bugs in running services. Helped work through the PCI-AE SA and make sure the company was processing credit information in a compliant manner.}
    \subsection{Volunteer Work}
        \cventry{2013}{Systems Administration}{\textsc{District 50 School}}{Sunnyland}{}{Helped local school restore and maintain information on servers after a power outage and system failure.}
        \cventry{2013}{Disaster Relief}{\textsc{Various}}{Washington}{}{Accepted, Organized, and Distributed Donations at local schools and churches.}
        \cventry{2014}{Debris Control}{\textsc{Peters Farms}}{Washington}{}{Cleared fields and ensured ground would be safe to plant crops.}
        \cventry{2015}{Event Support}{\textsc{Junior Achievement}}{Peoria, IL}{}{Worked with a team of individuals supporting financial literacy in children and teens that supports area schools. Provided support on a custom built PHP application simulating the stock market. Managed donor tables and acted as a broker for the simulation.}
